---
title: "Tilatkappale1"
output:
  html_document:
    toc: true
    toc_depth: 4


---

```{r echo=TRUE, message=FALSE, warning=FALSE}
# load data
setwd("~/GitHub/tilataso")
library(readr)
tilat<-read.csv(file="kategoriset.csv", header=TRUE)
```

### <span style="color:purple">Kuvailevat</span>



```{r message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}

# Define packages required by this script.
library(dplyr)
library(car)
library(ggplot2)
library(stargazer)
library(GGally)
library(tidyverse)
library(corrplot)
library(MASS)
library(knitr)
library(kableExtra)
library(tableone)
library(FactoMineR)
library(dplyr)
library(knitr)
library(DT)
library(xtable)
library(factoextra)
library(magrittr)
library(GGally)
library(ggplot2)
library(stringr)
library(tidyr)
library(MASS)
library(knitr)
library(kableExtra)
library(corrplot)
library(plotly)
library(dplyr)
summaryKable <- function(dataFrame) {
  require(dplyr)
  require(stringr)
  vect <- sapply(dataFrame, function(x) {
    if(!is.factor(x)) { 
      a <- c(quantile(x, probs = c(0,0.25,0.5), na.rm = T), 
             mean(x, na.rm = T),
             quantile(x, probs = c(0.75,1), na.rm = T)) %>% 
        formatC(format = "f", digits = 3) %>% 
        unname() 
    }
    
    if(is.factor(x)) {
      a <- sapply(1:5, function(y) 
            sum(x == levels(x)[y]) %>% 
            paste(levels(x)[y],. , sep = ":\ ")) 
      a <- c("Levels", a) %>% str_replace_all("NA: NA", "--")
    }
    
    return(a)
  })
  row.names(vect) <- c("Min", "1st Q", "Median", "Mean", "3rd Q", "Max")
  return(t(vect))
}
```


Valitsen muutaman jatkuvan muuttujan ja muutoin valitsen ne, joissa on alle 6 kategoriaa. Yhteenveto muuttujista:



```{r echo=TRUE, fig.align="center", fig.width=10, message=FALSE, warning=FALSE, warnings=FALSE}

colnames(tilat)[ apply(tilat, 2, anyNA) ]
tilat<-tilat[ , apply(tilat, 2, function(x) !any(is.na(x)))]


summaryKable(tilat[,1:218]) %>% 
  kable("html", align = "rrr", caption = "Data variable summary") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>%
scroll_box(height = "300px")

```



```{r echo=TRUE, fig.align="center", fig.width=10, message=FALSE, warning=FALSE, warnings=FALSE}


KreateTableOne = function(x, ...){
  t1 = tableone::CreateTableOne(data=x, ...)
  t2 = print(t1, quote=TRUE)
  rownames(t2) = gsub(pattern='\\"', replacement='', rownames(t2))
  colnames(t2) = gsub(pattern='\\"', replacement='', colnames(t2))
  return(t2)
}


```



### Yhteenveto kuolleisuuden mediaanin mukaan

```{r results='hide'}
#This is a very hacky function. If used within an RMarkdown document, KreateTableOne should be #called in a code chunk with \code{results='hide'} to hide the plain test results printed from #\code{tableone::CreateTableOne}. The resulting data frame should be saved as an object and used #in a second code chunk for formatted printing. Suggestions for improvement are welcomed.

tilatkat<-tilat[,1:218]%>%mutate_all(as.factor)

tilatkat$EMKUOL<-tilat$EMKUOLLJAKO
table1 = KreateTableOne(x=tilatkat, strata='EMKUOL')
```

```{r}

table1%>%
    kable("html", align = "rrr", caption = "Data variable summary strat by EMKUOL") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
  scroll_box(height = "300px" )

```




### Yhteenveto poistojen mediaanin mukaan

```{r results='hide'}
#This is a very hacky function. If used within an RMarkdown document, KreateTableOne should be #called in a code chunk with \code{results='hide'} to hide the plain test results printed from #\code{tableone::CreateTableOne}. The resulting data frame should be saved as an object and used #in a second code chunk for formatted printing. Suggestions for improvement are welcomed.

tilatkat2<-tilatkat
tilatkat2$EMPOIS<-tilat$EMPOISJAKO
table2 = KreateTableOne(x=tilatkat2, strata='EMPOIS')
```

```{r}

table2%>%
    kable("html", align = "rrr", caption = "Data variable summary strat by EMPOIS") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
  scroll_box(height = "300px" )

```

## MCA

```{r eval=FALSE, include=FALSE}
df<-tilat[,219:233]%>%mutate_all(as.numeric)
dfkat<-tilat[,1:150]%>%mutate_all(as.factor)

dfall<-cbind(dfkat,df)

DF<-dfall[c("Haastrooli_1OmEiosall_2OmOsall_3Esimies"                  
,"Tuotsuunta"                                                 
,"Karjut_astsiem"                                             
,"Tautsu"                                                     
,"Tautsuok"                                                   
, "Tautsu_012"                                                 
                                                                                                                 
,"JOU_pesu_0ei"                                               
                          
,"JOU_tyhjana_mi1vrk_0ei"                                     
,"PORSOSASTO_kertayt_0ei"                                     

                                   
,"PORS_pesu_0ei"                                              
,"PORS_pesuaine_0ei"                                          
,"PORS_desinf_0ei_1LIU_2KUIVA"                                
,"PORS_tyhjana_mi1vr_0ei"                                     
                                             
,"Raa_tuhoelain_1eipaase_0paaseesic"                          
, "Tuhoelmerkkeja_0kylla_1ei"                                  

                                         
,"Tuho_ohjelma"                                               
, "kissoja0on1ei"                                              
,"Kotielain_sikalaan_0kylla_1ei"                              
,"Vesi_1kunn_0oma"                                            
                                                    
, "Loisaika_1ennenpors_2_porskars"                             
,"Uusiryh"                                                    
, "Ton_tiheys_1aina_2jaetaan"                                  
, "Yhdistaggrtmp_1eiongelma_2tmp_3eitmp"                       
,"Muutelkaynn_0ei_1_satunn_2kaynnmuusaann"                    
,"maitokuume"                                                 
, "metriitti"                                                  
, "valuttelu"                                                  
,"mastiitti"                                                  
,"ontuma"                                                     
, "syomattomyys"                                               
,"kuume"                                                      
, "loukkaantuminen"                                            
,"AB_rutiinilaak"                                             
,"Oksitosiini_rutiinisti"                                     
, "Kaynnistys_rutiinisti"                                      
, "NSAID_porsituksessa_rutiini"                                
, "OMATENSIKOT_0EI_1KYLLa"                                     
                                                                                                 
, "Ensikk_yhdist_1ennsiem_2tiineena_3porsjalk_4tilantmuk"      
, "Kiimantark_ryhmakaytt"                                      
, "Kiimantarkalkaa_vrkvier"                                    
, "Kiimamerk_emakonselka"                                      
, "Kiimantark_postsiem"                                        
 , "Postsiem_ryhmakaytt_havainnointi"                           
, "Tiin_ultra2"                                                
                              
, "Kaynnistaminen_0ei_1rutiini_2yliaika_3ryhma_4satunnainen"   
, "Pesantekomatmaara_1runsas_2jnkv_3niukka"                    
, "Sisatutk_ennenoksitos"                                      
, "Porsitusaputekn_1empesu_2kaspesu_3kasine_4liukaste"         
, "PorsitusNSAID_0ei_1rutiinisti_2tarvittaessa"                
                   
, "Yksilöll_ruokinta"                                          
                                               
, "AS_em_kars"                                                 
, "AS_karspit"                                                 
, "AS_karslev"                                                 
, "AS_meluton"                                                 
, "AS_haittael_ei"                                             
, "AS_haittael_laatu"                                          
, "AS_ilma_aistin"                                             
, "AS_ilma_amm"                                                
                                               
                                                
, "AS_valaistus"                                               
, "AS_alusta12345"                                             
, "AS_alusta_5_laatu"                                          
,"AS_latt_rakenne1234"                                        
                                                                                           
,"AS_kuiv_mat12345"                                           
,"AS_kuiv_5_mika"                                             
, "AS_maara1234"                                               
, "AS_tonkimat123456"                                          
, "AS_tonkimat_6_mika"                                         
, "AS_mat_vaiht"                                               
, "AS_maara123"                                                
, "AS_annostelu1234"                                           
, "AS_lannanpoisto12"                                          
, "AS_rak_kunto"                                               
, "AS_latt_pitava")]

dfuusi<-cbind(DF,df)
tail(df)
res_mca = MCA(dfuusi, quanti.sup = c(74:88), graph = FALSE) 

```


```{r}
tilatkat<-tilat[,1:218]%>%mutate_all(as.factor)
tilatnum<-tilat[,219:233]%>%mutate_all(as.numeric)
tilat<-cbind(tilatkat,tilatnum)
res_mca = MCA(tilat, quanti.sup = c(219:233), graph = FALSE) 
```

To visualize the percentage of inertia explained by each MCA dimension:
```{r echo=TRUE, fig.align="center", message=FALSE, warning=FALSE}
eig.val <- res_mca$eig
barplot(eig.val[, 2], 
        names.arg = 1:nrow(eig.val), 
        main = "Variances Explained by Dimensions (%)",
        xlab = "Principal Dimensions",
        ylab = "Percentage of variances",
        col ="steelblue")
# Add connected line segments to the plot
lines(x = 1:nrow(eig.val), eig.val[, 2], 
      type = "b", pch = 19, col = "red")
```


```{r echo=TRUE, fig.align="center", fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
fviz_mca_var(res_mca, choice = "mca.cor", 
            repel = TRUE, # Avoid text overlapping (slow)
            ggtheme = theme_minimal())
```
To visualize the percentage of inertia explained by each MCA dimension:

```{r echo=TRUE, fig.align="center", fig.height=9, fig.width=13, message=FALSE, warning=FALSE}
fviz_mca_var(res_mca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE, # avoid text overlapping (slow)
             ggtheme = theme_minimal()
             )
```
```{r eval=FALSE, fig.align="center", message=FALSE, warning=FALSE, include=FALSE}
library(FactoInvestigate)
Investigate(res_mca)
```

