---
title: "Tilatkappale1"
output:
  html_document:
    toc: true
    toc_depth: 4
encoding: UTF-8

---

```{r echo=TRUE, message=FALSE, warning=FALSE}
# load data
setwd("~/GitHub/tilataso")
library(readr)
tilapieni<-read.csv(file="tilapieni.csv", header=TRUE)
```

### <span style="color:purple">Kuvailevat</span>



```{r message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}

# Define packages required by this script.
library(dplyr)
library(car)
library(ggplot2)
library(stargazer)
library(GGally)
library(tidyverse)
library(corrplot)
library(MASS)
library(knitr)
library(kableExtra)
library(tableone)
library(FactoMineR)
library(dplyr)
library(knitr)
library(DT)
library(xtable)
library(factoextra)
library(magrittr)
library(GGally)
library(ggplot2)
library(stringr)
library(tidyr)
library(MASS)
library(knitr)
library(kableExtra)
library(corrplot)
library(plotly)
library(dplyr)
summaryKable <- function(dataFrame) {
  require(dplyr)
  require(stringr)
  vect <- sapply(dataFrame, function(x) {
    if(!is.factor(x)) { 
      a <- c(quantile(x, probs = c(0,0.25,0.5), na.rm = T), 
             mean(x, na.rm = T),
             quantile(x, probs = c(0.75,1), na.rm = T)) %>% 
        formatC(format = "f", digits = 3) %>% 
        unname() 
    }
    
    if(is.factor(x)) {
      a <- sapply(1:5, function(y) 
            sum(x == levels(x)[y]) %>% 
            paste(levels(x)[y],. , sep = ":\ ")) 
      a <- c("Levels", a) %>% str_replace_all("NA: NA", "--")
    }
    
    return(a)
  })
  row.names(vect) <- c("Min", "1st Q", "Median", "Mean", "3rd Q", "Max")
  return(t(vect))
}
```


Valitsen muutaman jatkuvan muuttujan ja muutoin valitsen ne, joissa on alle 6 kategoriaa. Yhteenveto muuttujista:



```{r echo=TRUE, fig.align="center", fig.width=10, message=FALSE, warning=FALSE, warnings=FALSE}

tilapienikat<-tilapieni[1:76]%>%mutate_all(as.factor)
tilapieninum<-tilapieni[77:92]%>%mutate_all(as.numeric)
tilapieni<-cbind(tilapieninum,tilapienikat)

summaryKable(tilapieni) %>% 
  kable("html", align = "rrr", caption = "Data variable summary") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>%
scroll_box(height = "300px")
 
```

```{r echo=TRUE, fig.align="center", fig.width=10, message=FALSE, warning=FALSE, warnings=FALSE}
kuvat2<-tilapienikat
colnames(kuvat2)
gather(kuvat2) %>% ggplot(aes(value)) + facet_wrap("key", scales = "free") + geom_bar(fill="purple") + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8))+   scale_fill_manual("key")
```



```{r echo=TRUE, fig.align="center", fig.height=10, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
kor2<-tilapieninum


cor_fun <- function(data, mapping, method="pearson", ndp=2, sz=5, stars=TRUE, ...){

    data <- na.omit(data[,c(as.character(mapping$x), as.character(mapping$y))])

    x <- data[,as.character(mapping$x)]
    y <- data[,as.character(mapping$y)]

    corr <- cor.test(x, y, method=method)
    est <- corr$estimate
    lb.size <- sz* abs(est) 

    if(stars){
      stars <- c("***", "**", "*", "")[findInterval(corr$p.value, c(0, 0.001, 0.01, 0.05, 1))]
      lbl <- paste0(round(est, ndp), stars)
    }else{
      lbl <- round(est, ndp)
    }

    ggplot(data=data, mapping=mapping) + 
      annotate("text", x=mean(x), y=mean(y), label=lbl, size=lb.size,...)+
      theme(panel.grid = element_blank())
  }


ggpairs(kor2%>%mutate_all(as.numeric), 
        lower=list(continuous=wrap("smooth", colour="purple")),
        diag=list(continuous=wrap("barDiag", fill="purple")),
        upper=list(continuous=cor_fun),title="Graphical overview of the 17 variables")
```
```{r echo=TRUE, fig.align="center", fig.width=10, message=FALSE, warning=FALSE, warnings=FALSE}


KreateTableOne = function(x, ...){
  t1 = tableone::CreateTableOne(data=x, ...)
  t2 = print(t1, quote=TRUE)
  rownames(t2) = gsub(pattern='\\"', replacement='', rownames(t2))
  colnames(t2) = gsub(pattern='\\"', replacement='', colnames(t2))
  return(t2)
}


```



### Yhteenveto kuolleisuuden mediaanin mukaan

```{r results='hide'}
#This is a very hacky function. If used within an RMarkdown document, KreateTableOne should be #called in a code chunk with \code{results='hide'} to hide the plain test results printed from #\code{tableone::CreateTableOne}. The resulting data frame should be saved as an object and used #in a second code chunk for formatted printing. Suggestions for improvement are welcomed.


table1 = KreateTableOne(x=tilapieni, factorVars=colnames(tilapienikat), strata='EMKUOLLJAKO')
```

```{r}

table1%>%
    kable("html", align = "rrr", caption = "Data variable summary strat by EMKUOL") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
  scroll_box(height = "300px" )

```




### Yhteenveto poistojen mediaanin mukaan

```{r results='hide'}
#This is a very hacky function. If used within an RMarkdown document, KreateTableOne should be #called in a code chunk with \code{results='hide'} to hide the plain test results printed from #\code{tableone::CreateTableOne}. The resulting data frame should be saved as an object and used #in a second code chunk for formatted printing. Suggestions for improvement are welcomed.


table2 = KreateTableOne(x=tilapieni, factorVars=colnames(tilapienikat), strata='EMPOISJAKO')
```

```{r}

table2%>%
    kable("html", align = "rrr", caption = "Data variable summary strat by EMPOIS") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
  scroll_box(height = "300px" )

```



### Yhteenveto joku hylkays mukaan

```{r results='hide'}
#This is a very hacky function. If used within an RMarkdown document, KreateTableOne should be #called in a code chunk with \code{results='hide'} to hide the plain test results printed from #\code{tableone::CreateTableOne}. The resulting data frame should be saved as an object and used #in a second code chunk for formatted printing. Suggestions for improvement are welcomed.


table3 = KreateTableOne(x=tilapieni, factorVars=colnames(tilapienikat), strata='JOKUHYLK_01')
```

```{r}

table3%>%
    kable("html", align = "rrr", caption = "Data variable summary strat by JOKUHYLK") %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
  scroll_box(height = "300px" )

```
## MCA


```{r}

res_mca = MCA(tilapieni, quanti.sup = c(1:16), graph = FALSE) 
```

```{r}

summary(res_mca)
```


To visualize the percentage of inertia explained by each MCA dimension:
```{r echo=TRUE, fig.align="center", message=FALSE, warning=FALSE}
eig.val <- res_mca$eig
barplot(eig.val[, 2], 
        names.arg = 1:nrow(eig.val), 
        main = "Variances Explained by Dimensions (%)",
        xlab = "Principal Dimensions",
        ylab = "Percentage of variances",
        col ="steelblue")
# Add connected line segments to the plot
lines(x = 1:nrow(eig.val), eig.val[, 2], 
      type = "b", pch = 19, col = "red")
```


```{r echo=TRUE, fig.align="center", fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
fviz_mca_var(res_mca, choice = "mca.cor", 
            repel = TRUE, # Avoid text overlapping (slow)
            ggtheme = theme_minimal())
```


To visualize the percentage of inertia explained by each MCA dimension:

```{r echo=TRUE, fig.align="center", fig.height=9, fig.width=13, message=FALSE, warning=FALSE}
fviz_mca_var(res_mca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE, # avoid text overlapping (slow)
             ggtheme = theme_minimal()
             )
```

Simple bar plots can also be used to visualize contribution of variable categories. The top 12 variable categories contributing to the first and second dimension:

```{r echo=TRUE, fig.align="center", fig.height=4, fig.width=4, message=FALSE, warning=FALSE}
# Contributions of rows to dimension 1
fviz_contrib(res_mca, choice = "var", axes = 1, top = 12)
# Contributions of rows to dimension 2
fviz_contrib(res_mca, choice = "var", axes = 2, top = 12)
```

```{r eval=FALSE, fig.align="center", message=FALSE, warning=FALSE, include=FALSE}
library(FactoInvestigate)
res_mcacat<-MCA(tilapienikat,graph=FALSE)
Investigate(res_mcacat)
```

